Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-07 docs/evol.tex
started conclusions section

We explored the relation between defects with the size of a project version,
measured by the size of its {\sc jar} file by carrying out correlation tests
between the size and the defect counts for each project and its
version. The results, all statistically significant ($p \ll
0.05$) can be seen in Table~\ref{tbl:jarsizecorr}. The {\it Security
  High} category stands out by having a remarkably lower effect than
the other categories, even {\it Security Low} that nearly tops the
list.

@@

>>>>

We explored the relation between defects with the size of a project version,
measured by the size of its {\sc jar} file by carrying out correlation tests
between the size and the defect counts for each project and its
version. The results, all statistically significant ($p \ll
0.05$) can be seen in Table~\ref{tbl:jarsizecorr}. The {\it Security
  High} category stands out by having a remarkably lower effect than
the other categories, even {\it Security Low} that nearly tops the
list. In essense, a severe bug is introduced only when code that deals with
untrusted input is introduced in a application.

@@

In this work we analyzed a large software repository to examine the behavior
of security bugs. Specifically, we analyzed more than 260GB of interdependent
projcet versions to see how security bugs evolve over time, their
persistence, and their relation with other bug categories and the size in
terms of bytecode.
